Finalised versions of normalisation and threshold

### 2020-07-23 norm_threshold5.Rmd
adding recent simulation files

# Does normalisation work?
(Show with by comparing with maximum and showing for similar levels)

```{r smart_harmony}
library(ggplot2)
library(gravitas)
sm <- smart_meter10 %>% dplyr::filter(customer_id %in% c("10017936"))

@@

smart_harmony <- sm %>% 
  rank_harmony(harmony_tbl = harmonies,
               response = "general_supply_kwh", 
               dist_ordered = FALSE)

smart_harmony %>% kable()

smart_harmony %>% ggplot(aes(x = x_levels, y =  r)) + geom_point()

smart_harmony %>% ggplot(aes(x = facet_levels, y =  r)) + geom_point()
```

@@

@@

# Does it match with the threshold?
# Should they tally with each other?

## cricket data

```{r cricket}
cricket_data <- read_rds("data/cricket_data.rds")

harmonies_cric <- cricket_data %>% harmony(lgran = "over", ugran = "match", filter_in = c("lag_field", "over"), hierarchy_tbl = hierarchy_model)
```

```{r cricket_lag}
cricket_data <- read_rds("data/cricket_data.rds")
cricket_data %>%
  filter(over!=1) %>%
  prob_plot("over", "lag_field",
  hierarchy_model,
  response = "run_rate",
  plot_type = "violin",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)) +
   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("b") +
   theme(plot.title = element_text(face = "bold")) +  theme_minimal()
```

>>>>

```{r smart_harmony}

sm <- smart_meter10 %>% dplyr::filter(customer_id %in% c("10017936"))

@@

smart_harmony <- sm %>% 
  rank_harmony(harmony_tbl = harmonies,
               response = "general_supply_kwh", 
               dist_ordered = TRUE)

smart_harmony %>% 
  mutate(MMPD = round(MMPD, 3), max_pd = round(max_pd, 3)) %>% 
  mutate(rankn = row_number()) %>%
  rename("rankun" = "r") %>% kable()
```

```{r cricket_harmony}

cricket_data <- read_rds("data/cricket_data.rds")

.data <- cricket_data

harmonies_cric <- cricket_data %>% 
  harmony(lgran = "over",
          ugran = "match", 
          filter_in = c("lag_field", "over"),
          hierarchy_tbl = hierarchy_model)

cric_harmony <- cricket_data %>% 
  rank_harmony(harmony_tbl = harmonies_cric, 
               response = response,
               hierarchy_tbl = hierarchy_model,
               dist_ordered = TRUE) %>% 
  dplyr::filter(!(facet_variable=="over_inning"|x_variable =="over_inning"))

cric_harmony %>% 
  mutate(rankn = row_number()) %>%
  rename("rankun" = "r") %>% 
  mutate(MMPD = round(MMPD, 3), max_pd = round(max_pd, 3)) %>% 
  kable()
```

# Does normalisation work?

# Comparing similar levels

check (inning_match, over) and (lag_field, over) with similar levels.
(inning_match, over) is ranked above (lag_field, over). Let us see if it makes sense graphically.

## indicating difference in variation better than max (2 by 2)

```{r cric_graph_evidence}
p1 <- cricket_data %>%
  dplyr::filter(over!=1) %>%
  prob_plot("inning_match", "lag_field",
  hierarchy_model,
  response = "run_rate",
  plot_type = "quantile",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)) +
   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("") +
   theme(plot.title = element_text(face = "bold")) +  theme_minimal()

p2 <- cricket_data %>%
  dplyr::filter(over!=1) %>%
  prob_plot("lag_field", "inning_match",
  hierarchy_model,
  response = "run_rate",
  plot_type = "quantile",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)) +
   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("") +
   theme(plot.title = element_text(face = "bold")) +  theme_minimal()

ggpubr::ggarrange(p1, p2, nrow = 2, labels = c("MMPD = 0.08,  max_pd = 0.068", "MMPD = 0.06,  max_pd = 0.064")) + ggtitle("Normalised max better indicating difference")
```

## indicating difference in variation for harmonies with same levels (20 by 2)

```{r cric_samelev}

p1 <- cricket_data %>%
  dplyr::filter(over!=1) %>%
  prob_plot("over","lag_field",
  hierarchy_model,
  response = "run_rate",
  plot_type = "boxplot",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)) +
   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("MMPD = .058,  max_pd = 0.368") +
   theme(plot.title = element_text(face = "bold")) +  theme_minimal()

p2 <- cricket_data %>%
  dplyr::filter(over!=1) %>%
  prob_plot("over", "inning_match", 
  hierarchy_model,
  response = "run_rate",
  plot_type = "boxplot",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)) +
   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("MMPD = 0.039,  max_pd = 0.201") +
   theme(plot.title = element_text(face = "bold")) +  theme_minimal()
p1
p2

#ggpubr::ggarrange(p1, p2, ncol = 2, labels = c()) + ggtitle("Normalised max better indicating difference")
```

## How does it compare with taking unnormalised maximums?

```{r normalisation_work}
smart_harmony %>% mutate(lev = facet_levels*x_levels) %>% ggplot(aes(x = lev, y = r)) +geom_point()
smart_harmony %>% mutate(lev = facet_levels*x_levels, r_MMPD = row_number()) %>% ggplot(aes(x = lev, y = r_MMPD)) +geom_line()
```

@@

# How does the normalization work for the x-levels?

Let us fix the facet-level and see for different x-levels (31, 2) and (31, 7). Contrary to normalised max, non-normalised max ranks (31, 7) higher than (31, 2). Let us see which has higher variation.

```{r same-facet-level}
sm <- smart_meter10 %>%
filter(customer_id %in% c(10017936))
.data = sm
p1 <- sm %>% prob_plot("day_month", "wknd_wday", plot_type = "boxplot", symmetric = FALSE)  + 
  scale_y_log10()

p2 <- sm %>% prob_plot("day_month", "day_week", plot_type = "boxplot", symmetric = FALSE, quantile_prob = c(0.05, 0.25, 0.5, 0.75, 0.95)) + 
  scale_y_log10()

p1
p2
```

# How does the normalization work for the facet-levels?

Let us fix the x-level and see for different facet-levels.
(2, 24) and (7, 24). Contrary to normalised max, non-normalised max ranks (7, 24)  higher than (2, 24). Let us see which has higher variation.

```{r same-x-level}
sm <- smart_meter10 %>%
filter(customer_id %in% c(10017936))
.data = sm
p1 <- sm %>% prob_plot("wknd_wday", "hour_day", plot_type = "boxplot", symmetric = FALSE)  + 
  scale_y_log10()

p2 <- sm %>% prob_plot("week_month", "hour_day", plot_type = "boxplot", symmetric = FALSE, quantile_prob = c(0.05, 0.25, 0.5, 0.75, 0.95)) + 
  scale_y_log10()

p1
p2
```

@@

# Does it match with the threshold?

No

# Should they tally with each other?

Yes ideally. But given the number of permutations they are not matching. Tried with increasing the number of permutations - didn't help. Also, permutations taking very long since for each permutation MMPD is calcuated for every harmony pair at each step.

### 2020-07-23 simulations_MMPD6.Rmd
adding recent simulation files

# Comparing similar levels

check (inning_match, over) and (lag_field, over) with similar levels.
(inning_match, over) is ranked above (lag_field, over). Let us see if it makes sense graphically.

## indicating difference in variation better than max (2 by 2)

```{r cric_graph_evidence}
p1 <- cricket_data %>%
  dplyr::filter(over!=1) %>%
  prob_plot("inning_match", "lag_field",
  hierarchy_model,
  response = "run_rate",
  plot_type = "quantile",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)) +
   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("") +
   theme(plot.title = element_text(face = "bold")) +  theme_minimal()

p2 <- cricket_data %>%
  dplyr::filter(over!=1) %>%
  prob_plot("lag_field", "inning_match",
  hierarchy_model,
  response = "run_rate",
  plot_type = "quantile",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)) +
   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("") +
   theme(plot.title = element_text(face = "bold")) +  theme_minimal()

ggpubr::ggarrange(p1, p2, nrow = 2, labels = c("MMPD = 0.08,  max_pd = 0.068", "MMPD = 0.06,  max_pd = 0.064")) + ggtitle("Normalised max better indicating difference")
```

## indicating difference in variation for harmonies with same levels (20 by 2)

```{r cric_samelev}

p1 <- cricket_data %>%
  dplyr::filter(over!=1) %>%
  prob_plot("over","lag_field",
  hierarchy_model,
  response = "run_rate",
  plot_type = "boxplot",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)) +
   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("MMPD = .058,  max_pd = 0.368") +
   theme(plot.title = element_text(face = "bold")) +  theme_minimal()

p2 <- cricket_data %>%
  dplyr::filter(over!=1) %>%
  prob_plot("over", "inning_match", 
  hierarchy_model,
  response = "run_rate",
  plot_type = "boxplot",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)) +
   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("MMPD = 0.039,  max_pd = 0.201") +
   theme(plot.title = element_text(face = "bold")) +  theme_minimal()
p1
p2

#ggpubr::ggarrange(p1, p2, ncol = 2, labels = c()) + ggtitle("Normalised max better indicating difference")
```

## How does it compare with taking unnormalised maximums?

@@

@@

# How does the normalization work for the x-levels?

Let us fix the facet-level and see for different x-levels (31, 2) and (31, 7). Contrary to normalised max, non-normalised max ranks (31, 7) higher than (31, 2). Let us see which has higher variation.

```{r same-facet-level}
sm <- smart_meter10 %>%
filter(customer_id %in% c(10017936))
.data = sm
p1 <- sm %>% prob_plot("day_month", "wknd_wday", plot_type = "boxplot", symmetric = FALSE)  + 
  scale_y_log10()

p2 <- sm %>% prob_plot("day_month", "day_week", plot_type = "boxplot", symmetric = FALSE, quantile_prob = c(0.05, 0.25, 0.5, 0.75, 0.95)) + 
  scale_y_log10()

p1
p2
```

# How does the normalization work for the facet-levels?

Let us fix the x-level and see for different facet-levels.
(2, 24) and (7, 24). Contrary to normalised max, non-normalised max ranks (7, 24)  higher than (2, 24). Let us see which has higher variation.

```{r same-x-level}
sm <- smart_meter10 %>%
filter(customer_id %in% c(10017936))
.data = sm
p1 <- sm %>% prob_plot("wknd_wday", "hour_day", plot_type = "boxplot", symmetric = FALSE)  + 
  scale_y_log10()

p2 <- sm %>% prob_plot("week_month", "hour_day", plot_type = "boxplot", symmetric = FALSE, quantile_prob = c(0.05, 0.25, 0.5, 0.75, 0.95)) + 
  scale_y_log10()

p1
p2
```

@@

# Does it match with the threshold?

No

# Should they tally with each other?

Yes ideally. But given the number of permutations they are not matching. Tried with increasing the number of permutations - didn't help. Also, permutations taking very long since for each permutation MMPD is calcuated for every harmony pair at each step.

>>>>

## Number of levels and ranking

@@

## Comparing levels using simulated data

- MMPD should help choose the significantly different distributions only
- The ranking should be from most different to least different

Both of these should be checked again taking unnormalised statistic

## Scenario 1: Simulated same normal distributions for all combinations of the pair of cyclic granularities

## Scenario 2: Simulated same normal distributions for all x-levels within a facet, but different distributions across facets

## Scenario 3: Simulated different normal distributions for different x-levels but they do not vary across facets

# Scenario 4: Mixture of secenario 2 and 3

@@

@@
